plots

### 2024-11-04 draft_1.qmd
plots and tables

@@

@@

Plot 2: Performance based on Coverage Probability
![](cp_plot.jpeg)
## Performance based on CI width

@@

## Table 1: MSE results for n = 30, p = 3
## Table 2: Coverage Probability results for n = 30, p = 3
## Table 3: Confidence Interval width results for n = 30, p = 3
## Table 4: MSE results for n = 30, p = 10
## Table 5: Coverage Probability results for n = 30, p = 10
## Table 6: Confidence Interval width results for n = 30, p = 10

## Table 7: MSE results for n = 50, p = 3
## Table 8: Coverage Probability results for n = 50, p = 3
## Table 9: Confidence Interval width results for n = 50, p = 3
## Table 10: MSE results for n = 50, p = 10
## Table 11: Coverage Probability results for n = 50, p = 10
## Table 12: Confidence Interval width results for n = 50, p = 10

## Table 13: MSE results for n = 100, p = 3
## Table 14: Coverage Probability results for n = 100, p = 3
## Table 15: Confidence Interval width results for n = 100, p = 3
## Table 16: MSE results for n = 100, p = 10
## Table 17: Coverage Probability results for n = 100, p = 10
## Table 18: Confidence Interval width results for n = 100, p = 10

>>>>

-   which k's perform better

-   relation with n

When sample size is small, compared to most of the the selected shrinkage parameters OLS has very high MSE, especially when rho is high. Shrinkage parameters k1, k3, k7, k14, k18, k19 perform better (Table 1) in controlling the variance. For example, when $\rho$ = 0.99 ($\sigma^2$ = 1) The MSE of OLS is 8.408, while k1 (@hoerl1970ridge) has 1.658 and k18, k19 proposed by @chandnew has an MSE of 0.992. The performance difference between OLS and regularization parameters gets smaller as sample size increases. OLS produces more reliable predictions on larger datasets, although shrinkage parameters have a competitive advantage when rho is high. Regardless, of the sample size and colliniearity some k's like k10 and k11 do not show a significantly lower MSE than OLS.

@@

-   relation with p

 When the number of predictors is small, the MSE values for all methods are generally lower, with OLS performing reasonably well, especially in cases of low rho. However, shrinkage methods consistently outperform OLS, particularly when rho is higher.

For instance, when n = 50, p = 3, and rho = 0.85:

OLS has an MSE of 2.281, while k2 has an MSE of 1.283, demonstrating the superior performance of shrinkage parameters in controlling overfitting.

Larger Number of Predictors (p = 10): With a higher number of predictors, the OLS method becomes more prone to overfitting, especially when rho is high. Shrinkage methods, particularly k2, k5, and k6, show substantial reductions in MSE by introducing regularization to counteract overfitting and multicollinearity.

For instance, when n = 50, p = 10, and rho = 0.95:

OLS has a high MSE of 80.548, but k2 reduces this to 41.5, and k6 further reduces it to 24.373.

@@

Plot 2: Performance based on Coverage Probability ![](cp_plot.jpeg) \## Performance based on CI width

@@

## Overall Comparison MSE vs Coverage Probability

## Table 1: MSE results for n = 30, p = 3

## Table 2: Coverage Probability results for n = 30, p = 3

## Table 3: Confidence Interval width results for n = 30, p = 3

## Table 4: MSE results for n = 30, p = 10

## Table 5: Coverage Probability results for n = 30, p = 10

## Table 6: Confidence Interval width results for n = 30, p = 10

## Table 7: MSE results for n = 50, p = 3

## Table 8: Coverage Probability results for n = 50, p = 3

## Table 9: Confidence Interval width results for n = 50, p = 3

## Table 10: MSE results for n = 50, p = 10

## Table 11: Coverage Probability results for n = 50, p = 10

## Table 12: Confidence Interval width results for n = 50, p = 10

## Table 13: MSE results for n = 100, p = 3

## Table 14: Coverage Probability results for n = 100, p = 3

## Table 15: Confidence Interval width results for n = 100, p = 3

## Table 16: MSE results for n = 100, p = 10

## Table 17: Coverage Probability results for n = 100, p = 10

## Table 18: Confidence Interval width results for n = 100, p = 10

### 2024-11-04 plots.qmd
plots and tables

jpeg("cp_plot.jpeg", width = 2000, height = 1000, res = 150)

@@

>>>>

jpeg("cp_plot.jpeg", width = 2000, height = 800, res = 150)

@@

## Correlation plot

```{r}

jpeg("cor_plot.jpeg", width = 1800, height = 600, res = 150)
# Correlation plot

x <- as.matrix(mtcars[2:11])

# Install and load the corrplot package if not already installed
if (!require(corrplot)) install.packages("corrplot")
library(corrplot)

# Assuming 'data' is your data frame with numeric variables
# Calculate the correlation matrix
correlation_matrix <- cor(x, use = "complete.obs")

# Create a correlation plot with clustering
corrplot(correlation_matrix, method = "color", order = "hclust",
         addrect = 2, # Adds rectangles to emphasize clusters
         tl.col = "black", # Text label color
         tl.srt = 45, # Rotate text labels
         col = colorRampPalette(c("blue", "white", "red"))(200))
dev.off()

```
